Renal IV

### 2017-07-06 msk1.rmd
added sc

```
title: MSK I
author: Aaron Khoo
date: `r format(Sys.Date(%d %B %Y))`
output: pdf_document
```

@@

@@

> GP in Sarina (popn 6,000). Called by nurse working night shift. 72M brought in by *ambulance* found on bathroom floor. COuldn't get up, pain left hip, wife along.

@@

-  HPC: What caused him to fall such as seizure or slip? How did he fall? Land on anything? Remember the whole thing?
-  SOCRATES: site, onset, character, radiation, associations, time course, exacerbating/relieving factors, severity (in-depth HPC later).
-  See if anything else is wrong. Distracting injury could obfuscate.
-  Who is next of kin?

@@

-  MSK: fracture, muscular issues
-  GIT: constipation
-  CVS: shock, MI, stroke
-  Resp:
-  Neuro: nerve palsy, parkinsons?, lots of pain
-  Depression? Drugs? Alcohol

@@

-  Extrinsic
    -  Abdo/pelvic causes = {appendicitis, ovarian pathology, bowel pathology, endometriosis}.
    -  Local pathology such as inguinal/femoral herniae, lymph nodes.
    -  Spinal or sacroiliac referred pain.
    -  Meralgia paraesthetica (entrapment of lateral cutaneous nerve) or sciatica
    -  Malignancy
-  Intrinsic
    -  Soft tissue = {tendonitis, bursitis, snapping hip [movement of ITB over greater trochanter]}
    -  Joint = {osteoarthritis, rheumatoid, septic, synovitis}
    -  Bone = {hip/femur fracture, avascular necrosis}

@@

-  MSK: muscle weakness, pain in feet
-  Neuro: balance, parkinsons, poor vision
-  CVS: hypotension
-  External: clothes, external hazards, medications

@@

Priorities: Mx severe pain in left hip and get him walking again. Urgent: probs not

@@

-  Imaging: X-ray to view what is happening
-  FBC: check for anaemia?
-  CHEM20

@@

-  Pharmacologic: bisphosphanates (alendronate), calcitonin, denosumab (RANKL antag)
-  Vertebroplasty and kyphoplasty: for pt with persistent and severe focal back pain due to vertebral collapse
-  Dietary measures: adequate calcium and vit D
-  Physical therapy

>>>>

```
title: "MSK I"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output: pdf_document
```

@@

# Short case 1

> 43F bilateral shin pain, worse on L. Worsening past 2-3/12. Back from 1/12 training deployment army involving vigorous training.

Deep fibula N supplies anterior compartment of lower limb.

Pain origin: referred pain (sciatica can radiate to lower leg) [o/e could be no pain in the isolated area, but palpating the spine can demonstrate], dodgy gait, could be claudication, varicose veins, arthritis

To think of DDx: VINDICATE = {vascular, inflamm, neoplastic, degenerative/deficiency, idiopathic, congenital, autoimmune/allergic, traumatic, endocrine}

Questions to exclude red flags:

-  Have you been feeling tired and fatigued (Cancer)
-  Pain at rest or nocturnal, enough to disturb sleep
-  Weight loss, night sweats, or chills (Ca)
-  Hx of malignancy
-  Neuro compromise
-  Drugs or steroids (osteoporosis)
-  Immunosuppressed (infn; osteomyelitis)

Bone structure from exercise: Wolffs law, bones laid down where it is needed.

Hx questions:

-  HPC: SOCRATES, what do you think it is, why did you come in *today* as opposed to last week or yesterday,...
-  PMHx/PSHx
-  Medications (also gives indication for PMHx)/allergies/drugs
-  Fam Hx
-  Repro Hx
-  Social Hx: lifestyle, food, exercise, smoking

Menopause is a risk factor for osteoporosis.

MSK Ex: look $\rightarrow$ feel $\rightarrow$ move whilst comparing both sides

> Pain before deploying, has gradually worsened and now occurs with lighter exercise. Present at night.

Ex: Medial tibial stress syndrome has no swelling

Pathophysiology processes: fractures, necrosis

> Normal X-ray. She gets MRI

@@

> GP in Sarina (popn 6,000). Called by nurse working night shift. 72M brought in by *ambulance* found on bathroom floor. Couldn't get up, pain left hip, wife along.

@@

-  HPC: What caused him to fall such as seizure or slip? How did he fall? Land on anything? Remember the whole thing?
-  SOCRATES: site, onset, character, radiation, associations, time course, exacerbating/relieving factors, severity (in-depth HPC later).
-  Did you hit head
-  Remember everything, how did you fall?
-  See if anything else is wrong. Distracting injury could obfuscate.
-  Who is next of kin?
-  Social Hx to see how healthy he is

@@

-  MSK: fracture, muscular issues
-  GIT: constipation
-  CVS: shock, MI, stroke
-  Resp:
-  Neuro: nerve palsy, parkinsons?, lots of pain
-  Depression? Drugs diuretics can make pt get up at night? Alcohol

@@

-  Extrinsic
    -  Abdo/pelvic causes = {appendicitis, ovarian pathology, bowel pathology, endometriosis}
    -  Local pathology such as inguinal/femoral herniae, lymph nodes
    -  Spinal or sacroiliac referred pain
    -  Meralgia paraesthetica (entrapment of lateral cutaneous nerve) or sciatica
    -  Malignancy
-  Intrinsic
    -  Soft tissue = {tendonitis, bursitis, snapping hip [movement of ITB over greater trochanter]}
    -  Joint = {osteoarthritis, rheumatoid, septic, synovitis}
    -  Bone = {hip/femur fracture, avascular necrosis}

@@

-  MSK: muscle weakness, pain in feet
-  Neuro: balance, parkinsons, poor vision, inner ear pathology
-  CVS: hypotension
-  Renal: urinary incontinence can make people rush to the bathroom with increased risk of falling
-  External: clothes, external hazards, medications (polypharmacy)

@@

Priorities: Mx severe pain in left hip and vitals. Urgent: probs not

@@

-  Imaging: X-ray to view what is happening
-  FBC: check for anaemia?
-  CHEM20
-  ECG
-  Group and hold
-  COAGs

@@

-  Pharmacologic: bisphosphanates (alendronate), calcitonin, denosumab (RANKL antag)
-  Vertebroplasty and kyphoplasty: for pt with persistent and severe focal back pain due to vertebral collapse
-  Dietary measures: adequate calcium and vit D, smoking and alcohol
-  Physical therapy: weight bearing exercise
-  Hormone therapy
